---
title: "Homework 3 Problem 3"
author: "Leo Tadikonda"
format: pdf
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Types

R supports all of the main data types that we discussed in class during week 2. Strings in R are represented with quotation marks, before and after the object. Strings can contain letters, numbers, spaces, and punctuation. Change the my_name variable so that this code snippet prints your name.  

```{r string}

my_first_string <- "abc123"
print(my_first_string)
my_name = "Leo Tadikinda"
print(my_name)
```

## Arithmetic
We have already seen some examples of using R as a calculator to perform simple arithmetic but it can also do calculations with variables. Change the my_favorite_number variable to your favorite number. 

```{r number}

my_favorite_number <- 95 #your favorite number goes here!

a_new_number = my_favorite_number * 3 - 4
print(a_new_number)

a_new_number = (a_new_number ** 2)
a_new_number = a_new_number ** 2

cat("Is ", a_new_number, " a better number?")

```



## Conditional Expressions

R has built-in operators to evaluate comparisons between numbers and strings. Modify the following expressions so that they are true instead of false. 


```{r if}
print(3 > 2)
print(-6 > 5 + 7)
print(3 == 3)
print(12 == 12)
```


## Plotting 

One nice feature of the Markdown format is that it allows us to include R calculations and figures directly into our reports and presentations. The following code creates a short vector and then makes a plot of the values inside the vector. Change the values so that the dots decrease from left to right.  
```{r plot1}

my_first_vector <- c(15,12,5,2,1)
plot(my_first_vector)
```

